|

### 2023-07-16 paper/02-data.Rmd
shitton of work on supplement and figures

Table \ref{tab:track} displays a tracking data example for a play from the 2021 NFL regular season week six matchup between the Las Vegas Raiders and Denver Broncos, which ends with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack].
In addition, Figure \ref{fig:fig_field_raw} presents the locations of every Las Vegas (in black) and Denver (in orange) player on the field from this play at 1, 2, 3 and 4 seconds after the ball snap, with Maxx Crosby highlighted in blue.

[^crosbysack]: Game footage of this play is available at https://www.raiders.com/video/de-maxx-crosby-sacks-qb-teddy-bridgewater-for-a-loss-of-6-yards-nfl

>>>>

Table \ref{tab:track} displays a tracking data example for a [play](https://www.raiders.com/video/de-maxx-crosby-sacks-qb-teddy-bridgewater-for-a-loss-of-6-yards-nfl) from the 2021 NFL regular season week six matchup between the Las Vegas Raiders and Denver Broncos, which ends with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack].
In addition, Figure \ref{fig:fig_field_raw} presents the locations of every Las Vegas (in black) and Denver (in orange) player on the field from this play at 1, 2, 3 and 4 seconds after the ball snap, with Maxx Crosby highlighted in blue.

<!-- [^crosbysack]: Game footage of this play is available at https://www.raiders.com/video/de-maxx-crosby-sacks-qb-teddy-bridgewater-for-a-loss-of-6-yards-nfl -->

### 2023-07-16 paper/04-results.Rmd
shitton of work on supplement and figures

>>>>

```{r}
#| label: fig_features_combined
#| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of a successful pass rush play that results in a sack (left) and an unsuccessful pass rush play which results in a long pass attempt (right). The STRAIN for other pass rushers throughout each play is also displayed."
#| fig.width: 6
#| fig.height: 3.6
source(here("scripts", "15_fig_features_combined.R"))
fig_features_combined_bw
```

Figure \ref{fig:fig_features_combined}
